---
title: "CP3"
author: "Ledia Dobi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## library chunk
# First, install any packages that are not already installed
```{r libraries, include=FALSE}
required_packages <- c("dplyr", "readr", "tidyverse", "lmtest", "lubridate", "glmnet", "pls", "readxl", "GGally", "boot", "scales", "ggthemes", "caret")
install.packages(setdiff(required_packages, rownames(installed.packages())))
```

# Second, load all the packages
```{r load, include=FALSE}
invisible(lapply(required_packages, library, character.only = TRUE))
```

# Import Datasets
```{r import datasets, include=FALSE}
beauty <- read.csv("Beauty Care.csv")
hair <- read.csv("Hair.csv")
household <- read.csv("Household Care.csv")
makeup <- read.csv("Makeup.csv")
pet <- read.csv("Pet Care.csv")
skincare <- read.csv("Skincare.csv")
```

# View Datasets to see what we need to clean up before we combine
```{r view, include=FALSE}
view(beauty)
view(hair)
view(household)
view(makeup)
view(pet)
view(skincare)
```

# Cleaning Datasets
```{r clean, include=FALSE}

#Converting characters into numeric 
beauty_cleaned <- beauty %>%
  mutate(
    `Units.sold` = as.numeric(`Units.sold`),
    `Dollar.Sales.UD` = as.numeric(`Dollar.Sales.UD`),
    `Avg.Price.USD` = as.numeric(`Avg.Price.USD`),
  )

hair_cleaned <- hair %>%
  mutate(
    `Units.sold` = as.numeric(`Units.sold`),
    `Dollar.Sales.UD` = as.numeric(`Dollar.Sales.UD`),
    `Avg.Price.USD` = as.numeric(`Avg.Price.USD`),
    `YOY...Change` = as.numeric(`YOY...Change`)
  )

household_cleaned <- household %>%
  mutate(
    `Units.sold` = as.numeric(`Units.sold`),
    `Dollar.Sales.UD` = as.numeric(`Dollar.Sales.UD`),
    `Avg.Price.USD` = as.numeric(`Avg.Price.USD`),
    `YOY...Change` = as.numeric(`YOY...Change`)
  )

makeup_cleaned <- makeup %>%
  mutate(
    `Units.sold` = as.numeric(`Units.sold`),
    `Dollar.Sales.UD` = as.numeric(`Dollar.Sales.UD`),
    `Avg.Price.USD` = as.numeric(`Avg.Price.USD`),
    `YOY...Change` = as.numeric(`YOY...Change`)
  )

pet_cleaned <- pet %>%
  mutate(
    `Units.sold` = as.numeric(`Units.sold`),
    `Dollar.Sales.UD` = as.numeric(`Dollar.Sales.UD`),
    `Avg.Price.USD` = as.numeric(`Avg.Price.USD`),
    `YOY...Change` = as.numeric(`YOY...Change`)
  )

skincare_cleaned <- skincare %>%
  mutate(
    `Units.sold` = as.numeric(`Units.sold`),
    `Dollar.Sales.UD` = as.numeric(`Dollar.Sales.UD`),
    `Avg.Price.USD` = as.numeric(`Avg.Price.USD`),
    `YOY...Change` = as.numeric(`YOY...Change`)
  )
```

# Aggregate by year
```{r aggregation, include=FALSE}
# Hair
# Group by both 'Year' and 'Category'
hair_aggregated <- hair_cleaned %>%
  group_by(Year, Category) %>%
  summarize(
    total_units_sold = sum(`Units.sold`, na.rm = TRUE),
    total_dollar_sales = sum(`Dollar.Sales.UD`, na.rm = TRUE),
    mean_avg_price = mean(`Avg.Price.USD`, na.rm = TRUE),
    mean_yoy_change = mean(`YOY...Change`, na.rm = TRUE)
  ) %>%
  # Calculate the more accurate weighted average price
  mutate(
    weighted_avg_price = total_dollar_sales / total_units_sold
  )

view(aggregated_hair)

# Beauty
# Group by 'Year'
beauty_aggregated <- beauty_cleaned %>%
  group_by(Year) %>%
  summarize(
    total_units_sold = sum(`Units.sold`, na.rm = TRUE),
    total_dollar_sales = sum(`Dollar.Sales.UD`, na.rm = TRUE),
    mean_avg_price = mean(`Avg.Price.USD`, na.rm = TRUE),
  ) %>%
  # Add the 'Category' column with the value "Beauty"
  mutate(
    Category = "Beauty"
  ) %>%
  # Calculate the more accurate weighted average price
  mutate(
    weighted_avg_price = total_dollar_sales / total_units_sold
  )


# Household
# Group by 'Year'
household_aggregated <- household_cleaned %>%
  group_by(Year) %>%
  summarize(
    total_units_sold = sum(`Units.sold`, na.rm = TRUE),
    total_dollar_sales = sum(`Dollar.Sales.UD`, na.rm = TRUE),
    mean_avg_price = mean(`Avg.Price.USD`, na.rm = TRUE),
    mean_yoy_change = mean(`YOY...Change`, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  mutate(
    Category = "Household",
    weighted_avg_price = total_dollar_sales / total_units_sold
  )

# Makeup
# Group by 'Year'
makeup_aggregated <- makeup_cleaned %>%
  group_by(Year) %>%
  summarize(
    total_units_sold = sum(`Units.sold`, na.rm = TRUE),
    total_dollar_sales = sum(`Dollar.Sales.UD`, na.rm = TRUE),
    mean_avg_price = mean(`Avg.Price.USD`, na.rm = TRUE),
    mean_yoy_change = mean(`YOY...Change`, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  mutate(
    Category = "Makeup",
    weighted_avg_price = total_dollar_sales / total_units_sold
  )

# Pet
# Group by 'Year'
pet_aggregated <- pet_cleaned %>%
  group_by(Year) %>%
  summarize(
    total_units_sold = sum(`Units.sold`, na.rm = TRUE),
    total_dollar_sales = sum(`Dollar.Sales.UD`, na.rm = TRUE),
    mean_avg_price = mean(`Avg.Price.USD`, na.rm = TRUE),
    mean_yoy_change = mean(`YOY...Change`, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  mutate(
    Category = "Pet",
    weighted_avg_price = total_dollar_sales / total_units_sold
  )

# Skincare
# Group by 'Year'
skincare_aggregated <- skincare_cleaned %>%
  group_by(Year) %>%
  summarize(
    total_units_sold = sum(`Units.sold`, na.rm = TRUE),
    total_dollar_sales = sum(`Dollar.Sales.UD`, na.rm = TRUE),
    mean_avg_price = mean(`Avg.Price.USD`, na.rm = TRUE),
    mean_yoy_change = mean(`YOY...Change`, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  mutate(
    Category = "Skincare",
    weighted_avg_price = total_dollar_sales / total_units_sold
  )
```

# View aggregated Datasets
```{r view, include=FALSE}
view(beauty_aggregated)
view(hair_aggregated)
view(pet_aggregated)
view(skincare_aggregated)
view(household_aggregated)
view(makeup_aggregated)
```

# Reorder to make "Category" the second column
```{r reorder, include=FALSE}
#Hair
hair_aggregated <- hair_aggregated %>%
  select(Year, Category, everything())

#Beauty
beauty_aggregated <- beauty_aggregated %>%
  select(Year, Category, everything())

#Household
household_aggregated <- household_aggregated %>%
  select(Year, Category, everything())

#Makeup
makeup_aggregated <- makeup_aggregated %>%
  select(Year, Category, everything())

#Pet
pet_aggregated <- pet_aggregated %>%
  select(Year, Category, everything())

#Skincare
skincare_aggregated <- skincare_aggregated %>%
  select(Year, Category, everything())

```

# Remove Column Mean YOY Change
```{r remove mean_yoy_change, include=FALSE}

#Hair
hair_aggregated <- hair_aggregated %>%
  select(-mean_yoy_change)

#Household
household_aggregated <- household_aggregated %>%
  select(-mean_yoy_change)

#Makeup
makeup_aggregated <- makeup_aggregated %>%
  select(-mean_yoy_change)

#Pet
pet_aggregated <- pet_aggregated %>%
  select(-mean_yoy_change)

#Skincare
skincare_aggregated <- skincare_aggregated %>%
  select(-mean_yoy_change)
```

# View Datasets to ensure previous steps are reflected properly
```{r view, include=FALSE}
view(beauty_aggregated)
view(hair_aggregated)
view(pet_aggregated)
view(skincare_aggregated)
view(household_aggregated)
view(makeup_aggregated)
```

# Merge datasets
```{r merge, include=FALSE}

# Convert the 'Year' column to a character type in all dataframes
beauty_aggregated <- beauty_aggregated %>%
  mutate(Year = as.character(Year))

hair_aggregated <- hair_aggregated %>%
  mutate(Year = as.character(Year))

pet_aggregated <- pet_aggregated %>%
  mutate(Year = as.character(Year))

skincare_aggregated <- skincare_aggregated %>%
  mutate(Year = as.character(Year))

household_aggregated <- household_aggregated %>%
  mutate(Year = as.character(Year))

makeup_aggregated <- makeup_aggregated %>%
  mutate(Year = as.character(Year))

# Merge all the dataframes into a single, comprehensive dataframe
cpg <- bind_rows(
  beauty_aggregated,
  hair_aggregated,
  pet_aggregated,
  skincare_aggregated,
  household_aggregated,
  makeup_aggregated
)

# arrange the dataframe by Year and Category to make it easier to view
cpg <- cpg %>%
  arrange(Year, Category)

view(cpg)
```