---
title: "OLT Data Prep for Modeling"
author: "Ledia Dobi"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries


```{r libraries, include=TRUE}
required_packages <- c("dplyr", "readr", "tidyverse", "lmtest", "lubridate", "glmnet", "pls", "readxl", "GGally", "boot", "scales", "ggthemes", "caret")
install.packages(setdiff(required_packages, rownames(installed.packages())))
```

## Changing Factor on Unemployment Data


```{r Unemployment Data clean up, include=TRUE}
summary(cars)
```

## Aggregate years on Skincare and Makeup Data

You can also embed plots, for example:

```{r aaggregate years, include=TRUE}
plot(pressure)
```

## Change Axis on Skincare and Makeup Data

You can also embed plots, for example:

```{r axis change, include=TRUE}
plot(pressure)
```

## Combine Unemployment, Skincare, and Makeup Data

You can also embed plots, for example:

```{r combine datasets, include=TRUE}
plot(pressure)
```

## Create Dummy Variable for Recession Year

You can also embed plots, for example:

```{r dummy variable for recession, include=TRUE}
plot(pressure)
```
