---
title: "OLT Data Prep for Modeling"
author: "Ledia Dobi"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries


```{r libraries, include=TRUE}
required_packages <- c("dplyr", "readr", "tidyverse", "lmtest", "lubridate", "glmnet", "pls", "readxl", "GGally", "boot", "scales", "ggthemes", "caret")
install.packages(setdiff(required_packages, rownames(installed.packages())))
invisible(lapply(required_packages, library, character.only = TRUE))
```


## Changing Date on Unemployment Data


```{r Unemployment Data clean up, include=TRUE}
unemploy <- read.csv("Unemploy.csv")
class(unemploy$observation_date)
unemploy$observation_date <- ymd(unemploy$observation_date)
class(unemploy$observation_date)
unemploy$observation_date <- year(unemploy$observation_date)
view(unemploy)
```

## Changing Names of Columns


```{r renaming columns, include=TRUE}
colnames(unemploy) <- c("Year", "Unemploy_Rate")
head(unemploy)
```

## Group by Year, calculate mean of unemployment rate per year


```{r grouping by year, include=TRUE}
annual_unemploy <- unemploy %>%
  group_by(Year) %>%
  summarise(
    Annual_Avg_Rate = mean(Unemploy_Rate, na.rm = TRUE)
  )

head(annual_unemploy)
view(annual_unemploy)
```

## Aggregate years on Skincare and Makeup Data

You can also embed plots, for example:

```{r aaggregate years, include=TRUE}
skincare <- read.csv("Skincare.csv")
makeup <- read.csv ("Makeup.csv")

```

## Change Axis on Skincare and Makeup Data

You can also embed plots, for example:

```{r axis change, include=TRUE}
plot(pressure)
```

## Combine Unemployment, Skincare, and Makeup Data

You can also embed plots, for example:

```{r combine datasets, include=TRUE}
plot(pressure)
```

## Create Dummy Variable for Recession Year

You can also embed plots, for example:

```{r dummy variable for recession, include=TRUE}
plot(pressure)
```
